Psych 254 Replication Project Analysis

### 2016-07-01 analysis.Rmd
Minor changes to jedtan & salehi

  # If has project_info dataframe, add to all data
  if(exists("project_info")) { 
    all_project_info <- bind_rows(all_project_info,project_info) 
    # rm("project_info") # In case other file does not same
  } else {
    errors <- c(errors,paste0(project_key," is missing project_info"))
  }
}
```

>>>>

  # If has project_info dataframe, add to all data
  if(exists("project_info")) { 
    all_project_info <- bind_rows(all_project_info,project_info) 
    rm("project_info") # In case other file does not same
  } else {
    errors <- c(errors,paste0(project_key," is missing project_info"))
  }
}
```
